Figure: the scatterblob

### 2022-06-01 R/scatterblob.Rmd
pngs of color schemes

```{r}
my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
###############################################################
# start the pdf/png connection and set graphical parameters
###############################################################
plot_format <- "pdf"
# plot_format <- "svg"
# plot_format <- "png"

if (plot_format == "pdf") {
  pdf(file = here(outpath, "scatterblob_0.pdf"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, "scatterblob_0.svg"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, "scatterblob_0.png"),
      width = 8.25,
      height = 6,
      units = "in",
      res = 100,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(1.75, 9.75),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)),
     cex = 0.7,
     labels = c("Personal",
                "Lab \nmembers",
                "Other \nlabs",
                "The \ncommunity",
                "The \npublic"))
text(x = c(1, 3, 5),
     y = 0.5,
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10),
     cex = 0.7,
     adj = 1,
     labels = c("Elementary",
                "Low \nintermediate",
                "Intermediate",
                "Pre- \nAdvanced",
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(my_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_real[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_real,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)

@@

```{r}
my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)
###############################################################
# start the pdf/png/svg connection and set graphical parameters
###############################################################
plot_format <- "pdf"
# plot_format <- "png"
# plot_format <- "svg"

if (plot_format == "pdf") {
  pdf(file = here(outpath, "scatterblob_1.pdf"),
      width = 8.25,
      height = 6,
      bg = "transparent")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, "scatterblob_1.svg"),
      width = 8.25,
      height = 6,
      bg = "transparent")  
}
if (plot_format == "png") {
  png(file = here(outpath, "scatterblob_1.png"),
      width = 8.25,
      height = 6,
      units = "in",
      res = 100,
      bg = "transparent")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.5, nrow(my_data)),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 2, 4, 6, 8, 10, 12, 14, 15.5), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nintermediate",
                "Pre-\nintermediate",
                "Intermediate", 
                "Upper\nintermediate",
                "Pre-\nAdvanced",
                "Advanced",
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_seq[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_seq,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```

>>>>

```{r}
my_colors <- viridis::turbo(n = nrow(my_data), alpha = 0.9)

some_colors1 <- viridis::turbo(n = 30, alpha = 0.9)

some_colors2 <- viridis::magma(n = 30, alpha = 0.9)

plot(1:30, 1:30, col = some_colors2, pch = 8)
```

```{r}
my_colors <- some_colors1[c(3:4,
                           8,10,12,
                           20,21,22,23,24,
                           28,30)]
###############################################################
# start the pdf/png connection and set graphical parameters
###############################################################
#plot_format <- "pdf"
plot_format <- "svg"
#plot_format <- "png"

if (plot_format == "pdf") {
  pdf(file = here(outpath, "scatterblob_0.pdf"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, "scatterblob_0.svg"),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, "scatterblob_0.png"),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(1.75, 9.75),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)),
     cex = 0.7,
     labels = c("Personal",
                "Lab \nmembers",
                "Other \nlabs",
                "EEB \ncommunity",
                "All \nusers"))
text(x = c(1, 3, 5),
     y = 0.5,
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10),
     cex = 0.7,
     adj = 1,
     labels = c("Elementary",
                "Low \nintermediate",
                "Intermediate",
                "Pre \nAdvanced",
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(my_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_real[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_real,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)

@@

```{r}
some_colors3 <- viridis::turbo(n = 100, alpha = 0.9)
some_colors4 <- wesanderson::wes_palette("Zissou1", 75, type = "continuous")
some_colors5 <- wesanderson::wes_palette("Darjeeling1", 75, type = "continuous")
some_colors6 <- wesanderson::wes_palette("Darjeeling2", 75, type = "continuous")
some_colors7 <- wesanderson::wes_palette("Royal2", 75, type = "continuous")
plot(1:75, 1:75, col = some_colors7, pch = 8)
```

```{r}
my_colors <- some_colors3[c(5,15,
                           26,28,30,
                           68,72,76,80,84,
                           94,100)]
plot_name <- "scatterblob_1-viridis-turbo"
#my_colors <- some_colors4[round(my_data$y_real*10)-20]
#plot_name <- "scatterblob_1-zissou1"
# my_colors <- some_colors5[round(my_data$y_real*10)-20]
# plot_name <- "scatterblob_1-darjeeling1"
# my_colors <- some_colors6[round(my_data$y_real*10)-20]
# plot_name <- "scatterblob_1-darjeeling2"
# my_colors <- some_colors7[round(my_data$y_real*10)-20]
# plot_name <- "scatterblob_1-royal2"
###############################################################
# start the pdf/png/svg connection and set graphical parameters
###############################################################
plot_format <- "pdf"
# plot_format <- "png"
# plot_format <- "svg"

if (plot_format == "pdf") {
  pdf(file = here(outpath, paste0(plot_name, ".pdf")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "svg") {
  svg(filename = here(outpath, paste0(plot_name, ".svg")),
      width = 8.25,
      height = 6,
      bg = "white")  
}
if (plot_format == "png") {
  png(file = here(outpath, paste0(plot_name, ".png")),
      width = 8.25,
      height = 6,
      units = "in",
      res = 300,
      bg = "white")  
}
par(xpd = NA,
    mai = c(1.02, 1, 0.82, 4),
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5),
     y = c(0.4, 12.5),
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02)
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "EEB \ncommunity", 
                "All \nusers"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 1.5, 3, 4.5, 6, 7.5, 9, 10.5, 12 ), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nintermediate",
                "Pre\nintermediate",
                "Intermediate", 
                "Upper\nintermediate",
                "Pre\nAdvanced",
                "Advanced",
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(my_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y_seq[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y_seq,
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
